BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2014-09-25 Paper/BOAST.tex
Improved Paper

\begin{figure}
\lstset{style=BOAST,
        caption={BOAST code}, 
        label={lst:BOAST_procedure},
        numbers=left }
\begin{lstlisting}
n = Int("n")
ndat = Int("ndat")
x = Real("x", :dir => :in, :dim => [ Dim(0, n-1), Dim(ndat) ])
y = Real("y", :dir => :out, :dim => [ Dim(ndat), Dim(0, n-1) ])
p = Procedure("magicfilter", [n, ndat, x, y])
opn p
close p
\end{lstlisting}

@@

\begin{lstlisting}
SUBROUTINE magicfilter(n, ndat, x, y)
  integer(kind=4) :: n
  integer(kind=4) :: ndat
  real(kind=8), intent(in), dimension(0:n - (1), 1:ndat + 1 - (1)) :: x
  real(kind=8), intent(out), dimension(1:ndat + 1 - (1), 0:n - (1)) :: y
END SUBROUTINE magicfilter
\end{lstlisting}
\lstset{style=customc,
        caption={C output.},
        label={lst:BOAST_procedure_C} }

@@

>>>>

\begin{figure}
\lstset{style=BOAST,
        caption={BOAST code}, 
        label={lst:BOAST_procedure},
        numbers=left }
\begin{lstlisting}
n = Int("n", :dir => :in)
ndat = Int("ndat", :dir => :in)
x = Real("x", :dir => :in, :dim => [ Dim(0, n-1), Dim(ndat) ])
y = Real("y", :dir => :out, :dim => [ Dim(ndat), Dim(0, n-1) ])
p = Procedure("magicfilter", [n, ndat, x, y])
opn p
close p
\end{lstlisting}

@@

\begin{lstlisting}
SUBROUTINE magicfilter(n, ndat, x, y)
  integer(kind=4), intent(in) :: n
  integer(kind=4), intent(in) :: ndat
  real(kind=8), intent(in), dimension(0:n - (1), ndat) :: x
  real(kind=8), intent(out), dimension(ndat, 0:n - (1)) :: y
END SUBROUTINE magicfilter
\end{lstlisting}
\lstset{style=customc,
        caption={C output.},
        label={lst:BOAST_procedure_C} }

@@

The generated outputs in FORTRAN~\ref{lst:BOAST_procedure_FORTRAN} and
C~\ref{lst:BOAST_procedure_C} show the difference in meta-information
